\documentclass[pdftex,12pt,a4paper]{article}
\usepackage{PhysCoverSheet}
\lfoot{Prof S N Fisher/Dr N S Lawson \today}

\begin{document}
%%The box at the top
\begin{tabular*}{\textwidth}{| l | l | @{\extracolsep{\fill}}l| l  | }
\hline \tiny  &&& \\[0em] \normalsize
\Large{PHYS352} & Name \hspace{.4\textwidth} & \emph{Mark}  & \emph{Initials}   \\[1.2em]
\hline
\end{tabular*}

%%The Uni headder and departement
Lancaster University\hspace{\stretch{1}} Department Of Physics

%%The title of the sheet
\vspace{-0.5cm}
\begin{center}
\Large
\textbf{PHYS352 -- Short Project II:}\\
\textbf{Low Temperature Techniques}\\
\textbf{Lent Term 2010/11— Report}\\
\end{center}
\vspace{-0.5cm}
\noindent
\small$*$\charfill{\small$*$}$*$ \normalsize

THIS SHEET MUST BE ATTACHED TO YOUR FINAL REPORT -- please insert your
name at the top of this page. Do not submit your work in folders or plastic sleeves.

\textbf{Your log books and two hard copies of your report} should be placed in the
appropriate IN-BOX in the Physics Foyer no later than \textbf{5pm on Monday 21st March
2011} (week 20, the last week of Lent term). Work handed in after the above time and before
5pm on the following Monday will be subject to a 10\% point reduction of mark (e.g. work
scoring 65\% will be recorded as 55\%). Work handed in later than this will not count towards
your continuous assessment. \textbf{Electronic copies must also be submitted via LUVLE
by 5pm on Monday 21st March 2011}.

\textbf{Failure to submit substantial pieces of coursework without due cause can result
in an uncondoned fail mark which will prevent the award of an overall honors
degree.}

\emph{I declare that this submission is my own work. I have not submitted it in substantially the
same form towards the award of a degree or other qualification. It has not been written or
composed by any other person and all sources have been appropriately referenced or
acknowledged.}

Signed:%\dotfill
\hrule

\noindent
\small$*$\charfill{\small$*$}$*$ \normalsize

%%content would go here

\end{document}

